Model Samples Processing

### 2020-02-02 stats/model_sample_processing.Rmd
add model runs

model <- bind_rows(
  read_csv("../webppl/output/samples-reFactor-RE_mcmc-10_burn0_lag0_chain1.csv")%>%mutate(chain = 1)
)

@@

```{r}
model_pred <- model %>%
  filter(a == "modelPrediction")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred, "../saves/model_pred.rds")

>>>>

  m1 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain1.csv")%>%mutate(chain = 1)
  m2 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain2.csv")%>%mutate(chain = 2)
  m3 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain3.csv")%>%mutate(chain = 3)
  m4 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain4.csv")%>%mutate(chain = 4)
  m5 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain5.csv")%>%mutate(chain = 5)
  m6 <-read_csv("../webppl/output/samples-reFactor-RE_mcmc-200000_burn100000_lag10_chain6.csv")%>%mutate(chain = 6)

model <- bind_rows(
  m1,m2,m3,m4,m5,m6
)

saveRDS(m6, "../saves/m6.rds")

model <- bind_rows(
  readRDS("../saves/m1.rds"),
  readRDS("../saves/m2.rds"),
  readRDS("../saves/m3.rds"),
  readRDS("../saves/m4.rds"),
  readRDS("../saves/m5.rds"),
  readRDS("../saves/m6.rds")
)

@@

```{r}
model_pred_prag <- model %>%
  filter(a == "modelPrediction",
         b == "pragmatic")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_prag, "../saves/model_pred_prag.rds")

model_pred <- model %>%
  filter(a == "modelPrediction",
         b == "global")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred, "../saves/model_pred_global.rds")

model_pred_flat <- model %>%
  filter(a == "modelPrediction",
         b == "flat")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_flat, "../saves/model_pred_flat.rds")

model_pred_prior <- model %>%
  filter(a == "modelPrediction",
         b == "prior")%>%
  select(-a, -h)%>%
  rename(model = b, 
         parameter = c,
         alignment = d,
         item = e,
         age = f, 
         pred = g)

saveRDS(model_pred_prior, "../saves/model_pred_prior.rds")
